\textbf{Computational Fuzzy Extractors}

### 2013-02-15 CompFuzzExt.tex
sketches -> conductor
Removing yao and unpredictability entropy

\begin{construction}
Let $n$ be a security parameter and let $m>n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\sketch, \rec$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\sketch}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Output $s = (\vA, \vA X+w)$.
\\
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', s)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $s$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X' = \mathcal{I}_t(\vA, \vect{D})$\\
Set $X'_{n/2}$ be the first half bits of $X'$.		 
\item Output $X'_{n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\unp}_{\epsilon, s_{sec}}(W|\sketch(W)) \approx \Hoo(W)$.  Efficiency comes from the fact that up to some number of errors $t$, decoding is easy and thus $\mathcal{I}_t$ can be made polynomial-time.

@@

We will use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show there are many bits of $X$ that are unpredictable.  This says that if $\distLWE$ is hard then $X$ has many hardcore bits.  We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
\label{lem:many hardcore bits}
Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.  Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.  Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
\end{lemma}

@@

In the information theoretic setting, Dodis et. al.~\cite{DBLP:journals/siamcomp/DodisORS08} construct fuzzy extractors by using a secure sketch to perform (secure)~error correction and a randomness extractor to convert the distribution to close to uniform.  A similar paradigm seems desirable in the computational case: can a computational fuzzy extractor can be produced by a ``computational'' secure sketch and a randomness extractor~(which convert conditional HILL entropy to pseudorandom bits~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}).
}
\bibliographystyle{alpha}
\bibliography{crypto}
\appendix
\section{Background}
\subsection{Notions of Computational Entropy}
\label{sec:notionsEntropy}
In this sections we provide some further definitions of computational entropy.  HILL entropy is defined in \secref{sec:defCompFuzzyExtractors}.  HILL entropy generalizes the notion of indistinguishability.  Yao entropy~\cite{DBLP:conf/focs/Yao82a, barak-computational} generalizes the notion of compressibility.  Here we present the computational definition due to~\cite{DBLP:conf/eurocrypt/HsiaoLR07}:
\begin{definition}
\label{def:yao entropy}
For a distribution $X, Z$ we say that $X$ has Yao entropy at least $k$ conditioned on $Z$, denoted $H^{\yao}_{\epsilon, s}(X|Z)\geq k$, if for every pair of circuits $c,d$ of total size at most $s$ with the outputs of $c$ having length $\ell$,
\[
\Pr_{(x,z)\leftarrow (X,Z)}[d(c(x,z),z) = x]\leq 2^{\ell-k}+\epsilon
\]
\end{definition}
It should be clear that HILL entropy implies Yao entropy in both the unconditional and conditional case.  In the conditional case it is possible for Yao entropy to be significantly larger than HILL entropy~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.  We also use a less common notion called unpredictability entropy.  This measures an adversaries ability to recover a secret given some side information, see \defref{def:unp entropy}.
Unpredictability entropy is a notion between HILL and Yao entropy:
\begin{lemma}~\cite[Lemmas 8, 9]{DBLP:conf/eurocrypt/HsiaoLR07}\label{lem:hillimplyunpimplyyao}
\[ H^{\hill}_{\epsilon, s}(X|Z)\geq k \Rightarrow H^{\unp}_{\epsilon, s}(X|Z)\geq k\Rightarrow H^{\yao}_{\epsilon, s}(X|Z)\geq k.
\]
\end{lemma} 
\subsection{Unique Witness Relations}

@@

\begin{itemize}
\item $|W|$: The length of the source.  
\item $t$: Number of errors that can be supported.  
\item $n$: LWE security parameter (i.e., number of field elements in $X$), which must be greater than some minimum value $n_0$ for security.
\item $q$: The size of the field.  
\item $\rho$: The fraction of the field needed for error sampling.  
\item $m$: The size of each number of samples in the LWE instance.  
\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:conversion to unpredictability}).
\end{itemize}
We will split the source $|W|$ into $m$ blocks each of size $\rho q$~(that is, $|W| = m\log \rho q$).  We will ignore the parameter $|W|$ and focus on $t, n, q, \rho,$ and $m$.  As stated above we have three constraints:
\begin{itemize}
\item Maintain security of LWE.  If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + 3\gamma} m = \poly(n)$.  The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.  We ignore this effect and assume that $\rho q = 2n^{1/2+3\gamma}m$.
\item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-1)$.
\item Minimize entropy loss of the construction.  We will output $X_{1,...,k}$ so the entropy loss of the construction is $|W|-|X_{1,..., k}|$.  We want the entropy loss to be zero, that is, $|W| = |X_{1,..., k}|$.  Substituting, one has $m\log \rho q = k \log q$.
\end{itemize}
Collecting constraints we can support any setting where $t, n, q, \rho, m, k$ satisfy the following constraints~(for constants $d, f$):
\begin{align*}
n_0&< n -k \\
t&\leq d \log n\left(\frac{m}{n}-1\right)\\
q &= n^f\\
\rho q  &= 2n^{1/2+3\gamma}m\\
m\log \rho q &= k \log q
\end{align*}
Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:
\begin{align*}
n_0&< n - k\\
t&\leq d\log n\left(\frac{m}{n}-1\right)\\
m \log 2n^{1/2+3\gamma}m &= k \log n^f
\end{align*}
%\xnote{$ m \log 2n^{1/2+3\gamma}m = n \log n^f$}
This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.  However, the last equation may have no solution for $f$ constant.  Putting the last equation in terms of $f$ one has:
\begin{align*}
n_0&< n\\
t&\leq d\log n\left(\frac{ m }{n} -1\right)\\
%f \log n &= \frac{m}{n}\log 2n^2m\\
f &= \frac{m}{n}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
\end{align*}
To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.  Finally we assume that $t = d \log n(m/n-1)$~(this means we have only as many dimensions as necessary for polynomial time recovery):
\begin{align*}
n_0&< n\\
m &= \frac{(c+d)n \log n}{d \log n} = \frac{(c+d)n}{d}\\
f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{g(c+d)}{d}\frac{\log \frac{2(c+d)}{d} n^{3/2+3\gamma}}{\log n}
\end{align*}

>>>>

\begin{construction}
Let $n$ be a security parameter and let $m>n$.  %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\sketch, \rec$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\mathcal{I}_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\sketch}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Output $s = (\vA, \vA X+w)$.
\\
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rec}
\begin{enumerate}
\item \underline{Input}: $(w', s)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $s$ as $(\vA, \vect{C})$; let $\vect{D}=\vect{C}-w'$.
\item Let $X' = \mathcal{I}_t(\vA, \vect{D})$\\
Set $X'_{1,..., n}$ be the first half bits of $X'$.		 
\item Output $X'_{1,...,n}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

Intuitively, security comes from the computational hardness of decoding random linear codes from a high number of errors (introduced by $w$).  
In fact, we know that decoding a random linear code is NP-hard~\cite{berlekamp1978}; however, this statement is not sufficient for our security goal, which is to show  $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\sketch(W)) \approx \Hoo(W)$.  Efficiency comes from the fact that up to some number of errors $t$, decoding is easy and thus $\mathcal{I}_t$ can be made polynomial-time.

@@

We will use a result of Akavia, Goldwasser, and Vaikuntanathan~\cite{akavia2009} to show that $X$ has many hardcore bits.  This says that if $\distLWE$ is hard then $X$ has many hardcore bits.  We state their result for a general error distribution~(noting their proof does not consider the error distribution anywhere):
\begin{lemma}\protect{\cite[Lemma 2]{akavia2009}}
\label{lem:many hardcore bits}
Let $n>0$ be an integer, $q\geq 2$, let $\chi$ be an error distribution over $\zq$ and $k\leq n$ be an integer.  Let $\vA\in \zq^{m\times n} , X\in\zq^n$ and $E$ be distributed according to $\chi^m$.  Then $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., k}| \vA, \vA X+E )\geq k\log q$ assuming $\distLWE_{(n-k, m, q, \chi)}$.
\end{lemma}

@@

In the information theoretic setting, Dodis et. al.~\cite{DBLP:journals/siamcomp/DodisORS08} construct fuzzy extractors by using a secure sketch to perform (secure)~error correction and a randomness extractor to convert the distribution to close to uniform.  A similar paradigm seems desirable in the computational case: can a computational fuzzy extractor can be produced by a ``computational'' secure sketch and a randomness extractor~(which convert conditional HILL entropy to pseudorandom bits~\cite[Lemma 5]{DBLP:conf/eurocrypt/HsiaoLR07}).
}
\bibliographystyle{alpha}
\bibliography{crypto}
\appendix
\section{Background}
%\subsection{Notions of Computational Entropy}
%\label{sec:notionsEntropy}
%In this sections we provide some further definitions of computational entropy.  HILL entropy is defined in \secref{sec:defCompFuzzyExtractors}.  HILL entropy generalizes the notion of indistinguishability.  Yao entropy~\cite{DBLP:conf/focs/Yao82a, barak-computational} generalizes the notion of compressibility.  Here we present the computational definition due to~\cite{DBLP:conf/eurocrypt/HsiaoLR07}:
%\begin{definition}
%\label{def:yao entropy}
%For a distribution $X, Z$ we say that $X$ has Yao entropy at least $k$ conditioned on $Z$, denoted $H^{\yao}_{\epsilon, s}(X|Z)\geq k$, if for every pair of circuits $c,d$ of total size at most $s$ with the outputs of $c$ having length $\ell$,
%\[
%\Pr_{(x,z)\leftarrow (X,Z)}[d(c(x,z),z) = x]\leq 2^{\ell-k}+\epsilon
%\]
%\end{definition}
%It should be clear that HILL entropy implies Yao entropy in both the unconditional and conditional case.  In the conditional case it is possible for Yao entropy to be significantly larger than HILL entropy~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.  We also use a less common notion called unpredictability entropy.  This measures an adversaries ability to recover a secret given some side information, see \defref{def:unp entropy}.
%Unpredictability entropy is a notion between HILL and Yao entropy:
%\begin{lemma}~\cite[Lemmas 8, 9]{DBLP:conf/eurocrypt/HsiaoLR07}\label{lem:hillimplyunpimplyyao}
%\[ H^{\hill}_{\epsilon, s}(X|Z)\geq k \Rightarrow H^{\unp}_{\epsilon, s}(X|Z)\geq k\Rightarrow H^{\yao}_{\epsilon, s}(X|Z)\geq k.
%\]
%\end{lemma} 
%\subsection{Unique Witness Relations}

@@

\begin{itemize}
\item $|W|$: The length of the source.  
\item $t$: Number of errors that can be supported.  
\item $n$: LWE security parameter (i.e., number of field elements in $X$), which must be greater than some minimum value $n_0$ for security.
\item $q$: The size of the field.  
\item $\rho$: The fraction of the field needed for error sampling.  
\item $m$: The size of each number of samples in the LWE instance.  
\item $k$: The number of hardcore bits in $X$~(from \lemref{lem:many hardcore bits}).
\end{itemize}
We will split the source $|W|$ into $m$ blocks each of size $\rho q$~(that is, $|W| = m\log \rho q$).  We will ignore the parameter $|W|$ and focus on $t, n, q, \rho,$ and $m$.  As stated above we have three constraints:
\begin{itemize}
\item Maintain security of LWE.  If we assume GAPSVP and SIVP are hard to approximate within polynomial factors then \lemref{lem:uniform LWE decision} says that we get security for all $n$ greater than some minimum $n_0$ and $q = \poly(n)$ and $\rho q \geq 2 n^{1/2 + 3\gamma} m = \poly(n)$.  The only reason to increase $\rho q$ over this minimum amount (other than security) is if the number of errors in $W$ decreases with a slightly larger block size.  We ignore this effect and assume that $\rho q = 2n^{1/2+3\gamma}m$.
\item Maintain efficient decoding of Construction~\ref{cons:decoding algorithm}.  Using \lemref{lem:i t poly time}, this means that $t\leq d\log n(m/n-1)$.
\item Minimize entropy loss of the construction.  We will output $X_{1,...,k}$ so the entropy loss of the construction is $|W|-|X_{1,..., k}|$.  We want the entropy loss to be zero, that is, $|W| = |X_{1,..., k}|$.  Substituting, one has $m\log \rho q = k \log q$.
\end{itemize}
Collecting constraints we can support any setting where $t, n, q, \rho, m, k$ satisfy the following constraints~(for constants $d, f$):
\begin{align*}
n_0&< n -k \\
t&\leq d \log n\left(\frac{m}{n}-1\right)\\
q &= n^f\\
\rho q  &= 2n^{1/2+3\gamma}m\\
m\log \rho q &= k \log q
\end{align*}
Substituting $q = n^f$ and $\rho q = 2n^{1/2+3\gamma}m$ yields the following system of equations:
\begin{align*}
n_0&< n - k\\
t&\leq d\log n\left(\frac{m}{n}-1\right)\\
m \log 2n^{1/2+3\gamma}m &= k \log n^f
\end{align*}
%\xnote{$ m \log 2n^{1/2+3\gamma}m = n \log n^f$}
This is the most general form of our construction, we can support any $n, t, m$ that satisfy these equations for constants $d, f$.  However, the last equation may have no solution for $f$ constant.  Putting the last equation in terms of $f$ one has:
\begin{align*}
n_0&< n\\
t&\leq d\log n\left(\frac{ m }{n} -1\right)\\
%f \log n &= \frac{m}{n}\log 2n^2m\\
f &= \frac{m}{n}\frac{\log 2n^{1/2+3\gamma} m}{\log n}
\end{align*}
To ensure $f$ is a constant, we set $t = c \log n$ for some constant $c$ and that $k = n /g$ for some constant $g> 1$.  Finally we assume that $t = d \log n(m/n-1)$~(this means we have only as many dimensions as necessary for polynomial time recovery):
\begin{align*}
n_0&< n\\
m &= \frac{(c+d)n \log n}{d \log n} = \frac{(c+d)n}{d}\\
f &= \frac{m}{k}\frac{\log 2n^{1/2+3\gamma}m}{\log n} = \frac{g(c+d)}{d}\frac{\log \frac{2(c+d)}{d} n^{3/2+3\gamma}}{\log n}
\end{align*}
